### 2015-02-25 paper_30_measure.tex
mostly done with chapter 3

    \subsection{BALANCED SCORECARD}

        A common technique for organizations to measure themselves is a 
        balanced scorecard, first presented by Kaplan and 
        Norton \cite{kaplan1992}.

        Kaplan and Norton originally identified 4 characteristics
        for the balanced scorecard, but 
        A \textit{balanced scorecard} should contain the following six
        characteristics with the final 2 being optional 
        as they were presented later by Parmenter \cite{parmenter2010}
        and are not considered as part of the original balanced
        scorecard outlined by Kaplan and Norton \cite{kaplan1992,Kaplan2007}.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Internal Process
          \item Learning and Growth
          \item Employee Satisfaction
          \item Environment/Community
        \end{enumerate}

        Balanced scorecards are great for displaying the important information about
        an organization.  However, a balanced scorecard does not specify what
        exactly needs to be tracked.  It is also not specific to an SDO and 
        it does not produce a single number.

        This info comes from .

    \subsection{PROJECT MANAGEMENT MEASUREMENT}
        According to Putnam and Myers in \cite{Putnam2013}, the 5 core measurements for managing software
        projects are:

        \begin{enumerate}
            \item \textbf{Quantity of function} usually measured in terms of size (such as source lines of code or function points), that ultimately execute on the computer
            \item \textbf{Productivity} as expressed in terms of the functionality produced for the time and effort expended
            \item \textbf{Time} the duration of the project in calendar months
            \item \textbf{Effort} the amount of work expended in person-months
            \item \textbf{Reliability} as expressed in terms of defect rate (or its reciprocal, mean time to defect)
        \end{enumerate}
        However, these measurements don't focus on the entire SDO. They say nothing about the availablity of the software infrastructure or the satisfaction of the users.

        \begin{description}
          \item[Time] This measurement can be hours, days, weeks, or months.  the time increment does not matter as long as it is consistent.
          \item[Effort] This measurement is person-months, person-weeks, or person-days.
          \item[Quality] This measurement is the defect rate (defects per time period).
          \item[Amount of Work] This measurement has the same units as Effort above. 
          \item[Process Productivity] look into this a bit further
          \item[Function Points] find a definition and a comparison with story points
          \item[Story Points] Look in some agile book
        \end{description}

        Chapter 7 of \cite{Putnam2013} contains some equations to calculate and relate
        these measures. Those equations will be studied and evaluated.

    \subsection{MEASURING OTHER ASPECTS OF AN SDO}

        It is important to note that software departments do not just
        develop software.  The department has many other duties
        including: deploying software, installing server hardware/software,
        writing documentation, surveying users, research, innovation,
        education and other common business duties.

    \subsection{COMBINING THE MEASURES}

        How can the PIs, RIs, KRIs, and KPIs be combined to form a single
        value called an MPI (Master Performance Indicator)?  The field
        of sports analytics also has numerous techniques for combining
        multiple indicators to produce a single number \cite{Cervone2014}.

making decisions based upon historical data.

Data Driven Software Engineering not Data Driven Software Development

>>>>

    \subsection{BALANCED SCORECARD}
    \label{sec:bsc}

        Developed in 1992 by Robert S. Kaplan and David P. Norton, the 
        \textit{balanced scorecard}  is a set of measures that
        give management a quick and comprehensive view of the
        organization \cite{kaplan1992}.  Originally created as an
        extension to the already existing financial measures, the
        balanced scorecard expanded the measures to include: 
        customer focus, internal process, and learning/growth. 
        This gave organizations a more comprehensive view that was
        not strictly financial.  It allows an organization to focus
        on long-term strategic goals instead of just short-term goals.
        As a result of the strategic focus, the balance scorecard
        rapidly gained widespread adoption
        among businesses \cite{Kaplan2007}.

        In 2010, David Parmenter \cite{parmenter2010} added 2 more
        characteristics to the balanced scorecard: employee satisfaction
        and environment/community.  This results in a total of 6 
        characteristics for the balanced scorecard.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Internal Process
          \item Learning and Growth
          \item Employee Satisfaction\footnote{\label{ft:bsc} These 2 
                characteristics are not a part of the original balanced 
                scorecard presented by Kaplan and Norton in 1992.  
                They  were added later by Parmenter \cite{parmenter2010}. }
          \item Environment/Community\textsuperscript{\ref{ft:bsc}}
        \end{enumerate}

        Balanced scorecards are great for easily displaying the 
        important information about
        an organization.  The downside is a balanced scorecard does not specify what
        exactly needs to be tracked. It can be very difficult to determine exactly
        what PIs, RIs, KRIs and/or KPIs to track in a balanced scorecard. 
        It just specifies 6 broad categories.
        It is also not specific to an SDO and 
        it does not produce a single number.  However, any new measurement
        technique for an organization should be compared with the balanced
        scorecard.

    \subsection{PROJECT MANAGEMENT MEASUREMENT}
    \label{sec:pm}
        A final strategy to measure an SDO is focused on the aspect of
        project management. Project management is the guidance
        applied to a project to ensure an effective and efficient
        completion.  Proper project management will ensure all steps
        of the SDLC
        continue to progress and all obstacles are handled
        in a timely fashion.  
        According to Putnam and Myers in \cite{Putnam2013}, 
        the 5 core measurements for managing software
        projects are:

        \begin{enumerate}
            \item \textbf{Quantity of function} usually measured in terms of size (such as source lines of code), that ultimately execute on the computer
            \item \textbf{Productivity} as expressed in terms of the functionality produced for the time and effort expended
            \item \textbf{Time} the duration of the project in calendar months
            \item \textbf{Effort} the amount of work expended in person-months
            \item \textbf{Reliability} as expressed in terms of defect rate (or its reciprocal, mean time to defect)
        \end{enumerate}

        A \textit{process productivity} number is calculated based entirely
        off aspects of the SDLC and the 5 core measurements.  It is a number
        targeted at project teams working on the SDLC.

    \subsection{A SIMPLER MEASUREMENT}

        It is important to note that SDOs do not just
        develop software.  An SDO has many other duties
        including: deploying software, installing server hardware/software,
        writing documentation, surveying users, research, innovation,
        education and other common business duties.  Thus it is
        important to measure as many duties as possible.

        How can the PIs, RIs, KRIs, and KPIs be combined to form a single
        value called an MPI (Master Performance Indicator)?

### 2015-02-25 paper_40_mpi.tex
chapter 3 work
mostly done with chapter 3

\section{MASTER PERFORMANCE INDICATOR (MPI)}

@@

@@

            \begin{longtable}{p{4cm}p{10cm}}
                % pairs: absolute number (percentage)

@@

>>>>

\section{MASTER PERFORMANCE INDICATOR (MPI)}
\label{sec:MPI}

@@

            \begin{description}
              \item[Function Points] find a definition and a comparison with story points
              \item[Story Points] Look in some agile book
            \end{description}

@@

            \begin{longtable}{p{4cm}p{10cm}}

@@

        \subsubsection{MPI VS. BALANCED SCORECARD}
            Section \ref{sec:bsc} discusses the characteristics of the 
            balanced scorecard.  Table \ref{tab:bsc} presents a
            comparison of the characteristics of a balanced scorecard
            versus MPI.
            As the newer 2 characteristics of a balanced scorecard
            have only existed since 2010 and the adoption is limited,
            the comparison will only be against the original 4 balanced
            scorecard characteristics.

             \begin{longtable}{p{3cm}p{1cm}p{10cm}}
                % pairs: absolute number (percentage)

                \toprule%
                 \centering%
                 {\bfseries Balanced Scorecard}
                 & {\bfseries MPI?} 
                 & {\bfseries Explanation} \\

                \cmidrule[0.4pt](r{0.125em}){1-1}%
                \cmidrule[0.4pt](lr{0.125em}){2-2}%
                \cmidrule[0.4pt](lr{0.125em}){3-3}%
                % \midrule
                \endhead

                Financial & No & MPI does not address financial as it is best suited 
                    for an organization that treats software development as a fixed,
                    budgeted expense. If the budget is fixed, MPI provides a number
                    to indicate the amount of value for that fixed budget.  \\
                \myrowcolour%
                Customer Focus & Yes & MPI includes a customer survey which is 
                    completely customer focused.\\
                Internal Process & Yes & MPI is highly focused on internal processes.
                    The MPI elements of schedule and requirement are completely
                    focused on how reality meets the expected process. MPI is
                    negatively impacted when internal processes are followed. \\
                \myrowcolour%
                Learning/Growth & No & MPI does not address this characteristic. \\

                \caption{BALANCED SCORECARD VERSUS MPI}
                \label{tab:bsc}
            \end{longtable}

        \subsubsection{MPI VS. PROJECT MANAGEMENT MEASUREMENT}
            Previously in Section \ref{sec:pm}, the project management
            measurement was presented.   Its greatest limitation is the lack of
            focus on the entire SDO.  Project management measurement says 
            nothing about the availability of the software infrastructure
            or the satisfaction of the users.  It is not near as comprehensive
            as either the balanced scorecard or MPI. Actually, MPI incorporates
            the 5 core measurements from project management.
            Plus, the process productivity
            number is less suitable for upper management and more
            suitable for project teams.  Although it does provide a single
            process productivity number, it is does not have the same focus
            as MPI.

### 2015-02-25 paper_80_conclusion.tex
mostly done with chapter 3

>>>>

As shown in Table \ref{tab:bsc}, MPI is currently not addressing 2 characteristics of the balanced scorecard.  If the SDO does not operate on a fixed budget, MPI could be 
expanded to include another element for financial data. The challenge arises when
determining how to relate the SDO performance to finances.  The most likely scenario
would be a method to either select or predicted the expected software sales
for a month.  Then every month create an MPI element score that reflects
how much the expected sales were exceeded or missed.  The other missing
balanced scorecard characteristic is learning and growth.  Those are very difficult
to quantitatively measure.  In this case some possible data points might be:
hours of training, number of training courses, number of employees receiving
training, number of promotions, or another measure centered around training
courses and career growth.  Again, once data exists, the problem becomes finding
a baseline and measuring with respect to that baseline.
